S2 Appendix

### 2021-03-23 src/s2.Rmd
editing changes

The below maps plot the Pareto exponents for all the countries included in our data 
set for the years 2000, 2005, 2010 and 2010. The quantiles of the yearly exponent 
distribution are used for the maps with the first quantile always representing 
the countries with the of the smallest Pareto exponent.

>>>>

The below maps plot the Pareto exponents corrected as per Gabaix and Ibragimov (2011) for all the countries included in our data 
set for the years 2000, 2005, 2010 and 2010. The quantiles of the yearly exponent 
distribution are used for the maps with the first quantile always representing 
the countries with the of the smallest Pareto exponent.
